Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-09 draft/accordionComplexSurfaces.tex
Added some proofs.

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}
\begin{proof}
 \pierreguy{TO DO}
\end{proof}

@@

\begin{proof}
See \fref{fig:kissings} and \fref{fig:kissingVSCrossing}.
\pierreguy{Complete this proof using the pictures.}

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissings}}
	\caption{Two representations of a pair of kissing walks.}
	\label{fig:kissings}
\end{figure}

@@

@@

\begin{proposition}
\label{prop:purity}
The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
\vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
\end{proposition}

>>>>

\begin{lemma}
\label{lemm:accordionsAreCurvesOfWalks}
Let~$\gamma$ be a~$\dissection_{\bar Q}$-accordion.  There exists a unique undirected walk~$\walk(\gamma)$ such that we have~$\curveof(\walk(\gamma)) = \gamma$.
\end{lemma}
\begin{proof}
We can assume that~$\gamma$ intersects itself and the arcs of~$\dissection_{\bar Q}$ transversaly and minimally, in the sense that~$\gamma$ does not cross an arc twice in succession in opposite directions.
Then~$\gamma$ is completely determined by its sequence of intersection points with the arcs of~$\dissection_{\bar Q}$, since the dissection is cellular.
Two successive intersection points in this sequence define an angle between two arcs of~$\dissection_{\bar Q}$, which correspoinds to an arrow in~$\bar Q$.
Thus the sequence of intersection points defines a walk~$\walk(\gamma)$ on~$\bar Q$.
By construction, we have that~$\curveof(\walk(\gamma)) = \gamma$.

Is also follows from construction above and from Definition~\ref{def:curveOfAWalk} that~$\walk(\curveof(\omega)) = \omega$ for any walk~$\omega$.
This finishes the proof.
\end{proof}

@@

\begin{proof}
A kiss between two walks~$\omega$ and~$\omega'$ is depicted on \fref{fig:kissings}.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{kissings}}
	\caption{Two representations of a pair of kissing walks.}
	\label{fig:kissings}
\end{figure}
The left hand side of the picture is as in \fref{fig:kissing}, and the right hand side is simply a different representation of it.
On the surface~$\surface(\bar Q)$, the dual dissections~$\dissection$ and~$\dissection\dual$ are as on \fref{fig:kissingVSCrossing} (on the right hand side).

@@

The curves~$\curveof(\omega)$ and~$\curveof(\omega')$ on the surface follow~$\omega$ and~$\omega'$ on the picture.
It is then clear that~$\omega$ and~$\omega'$ kiss if and only if~$\curveof(\omega)$ and~$\curveof(\omega')$ cross.

@@

\begin{proposition}
\label{prop:purity}
The non-kissing complex~$\NKC$ and the non-crossing complex~$\NCC[\dissection_{\bar Q}, {\dissection_{\bar Q}}\dual]$ are pure of dimension~$3|Q_0| - |Q_1|$.
\vincent{This is wrong. We need to count the infinite straight walks. I propose the next statement instead.}
\pierreguy{I agree.}
\end{proposition}
